\section{Abstract}
The project addresses the two-dimensional, standard, linear wave equation, with damping.
\begin{equation}
 \frac{\partial^2 u}{\partial t^2} + b\frac{\partial u}{\partial t} = \frac{\partial}{\partial x} \left( q(x,y)\frac{\partial u}{\partial x} \right)
 + \frac{\partial}{\partial y} \left( q(x,y)\frac{\partial u}{\partial y} \right) + f(x,y,t)
 \label{wave_eq}
\end{equation}
We have solved this wave equation by the finite difference method. First we implemented the problem by scalar computation to get a working program, 
and when we were pretty sure our program worked we vectorized the problem for speed. We had three tests we could run to verify our code; we contructed a test case with constant solution,
we made an exact 1D solution (plug wave) and we manufactured a standing wave. The latter test does not give an exact solution of the discrete equations, so we had to do an
empirical analysis of the convergence. The expected error to the standing wave is 
\begin{equation}
 E = Ch^2
\end{equation}
where C s a constant chosen to be compatible with the stability criterion, and h is a common discretization parameter to be varied.\\
We used mayavi to visualize the 2D solution in 3D-plots.\\
The program can be used to simulate waves on water, and we chose to do this while looking at different sea-bottom shapes. We experimented a little as well,
and ended up with a simulation of rain on a pond. The rain was made by letting the source term be a Gauss-function with random position and size. 




